\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/figures.tex

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %Multicore Implementation  &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,
        ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
        without needing an inline element in the ISP network.
        ``Handles asymmetric routes'' refers to schemes that work when only one direction (either client to decoy or decoy to server) is seen by the station.
        ``Replay attacks'' refers to censors who may replay/preplay previous messages or actively probe
        the protocol.
        ``Traffic analysis'' includes latency, inter-packet timing, and website fingerprinting.
        ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
        or upload arbitrarily large content.}
    \label{tab:compare}
\end{table*}
}

>>>>

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resistant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %Multicore Implementation  &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,
        ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
        without needing an inline element in the ISP network.
        ``Handles asymmetric routes'' refers to schemes that work when only one direction (either client to decoy or decoy to server) is seen by the station.
        ``Replay attacks'' refers to censors who may replay/preplay previous messages or actively probe
        the protocol.
        ``Traffic analysis'' includes latency, inter-packet timing, and website fingerprinting.
        ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
        or upload arbitrarily large content.}
    \label{tab:compare}
\end{table*}
}
